\documentclass[titlepage]{article}
\usepackage{array}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{listings}

\begin{document}

\author{Stevan Stanisic and Santana Mach}
\title{COMP 7615 - Assignment 4 \\ Pong and Maze Reloaded}
\date{Nov 21, 2011}
\maketitle{}

\pagebreak

\section{Introduction}

Part 1: Pong with Sound \\
The background music is recycled from Spoon's adventure and will play any time the ball is in play. The bounce sound will play any time the ball bounces off a paddle or wall. \\
\\
Part 2: Maze Reloaded \\
A footstep sound has been added to play any time the user is moving, as has a "faceplant" sound any time the user collides with a wall. The user can now press the B key or Dpad Down
on the gamepad to toggle background music on/off. The music will change to a different piece if the user toggles day/night and will be attenuated if fog is toggled on. Finally, the music volume
is also modulated based on the user's distance to Cartman. \\
\\
Part 3: Pong Reloaded \\
A simple high-score system has been added. The menu can be displayed by pressing the M key or Y on the gamepad. The player who wins will have their score added to the list if it is
high enough and the score is saved between games.  Additionally, if a player is signed in to Live, their name will be used for player 1 and they could make it on to the high score list. \\
\\
\\
\section{Controls for Maze Reloaded}
Keyboard and Mouse: \\
ESC - Exit \\
WASD - Movement \\
Arrow Keys or Mouse - Camera \\
Plus and Minus (not numpad) - Zoom in out (implemented like sample) \\
B - Background music toggle \\
M - Minimap toggle \\
G - Fog toggle \\
F - Flashlight toggle \\
L - Day/Night toggle \\
C - Clipping toggle \\
Home - Reset to maze start \\
R - Generate new maze \\
\\
XBOX 360 Controller: \\
Back - Exit \\
Left Stick - Movement \\
Right Stick - Camera \\
Left and Right Triggers - Zoom in out (implemented like sample) \\
Start - Minimap toggle \\
Dpad Down - Background music toggle \\
A - Fog toggle \\
B - Flashlight toggle \\
X - Day/Night toggle \\
Y - Clipping toggle \\
Left Shoulder - Reset to maze start \\
Right Shoulder - Generate new maze \\

\end{document}